Labeled object representation and manipulation with ITK

### 2007-08-10 article/Article.tex
more of the article
darcs-hash:20070810084508-2fc9d-05f2c848b6f60e9e7a3c1103260ad4c6c77faf57.gz

ITK is currently lacking a good way to manipulate the binary objects. That contribution I hope to have mostly
filled that lack.

>>>>

ITK is currently lacking a good way to manipulate the binary objects. With that contribution I hope to have mostly
filled that lack.

\section{Acknowledgments}
I thank Richard Beare for his suggestion to use the run length encoding to represent the binary objects, and Julien Jomier for his help for the choice to {\em not} use the {\em SpatialObject} class as base class of the {\em LabelObejct} class.

I thank Dr Pierre Adenot and MIMA2 confocal facilities
(\url{http://mima2.jouy.inra.fr}) for providing the 3D test image.
I am grateful to the INRA MIGALE bioinformatics platform
(\url{http://migale.jouy.inra.fr}) for providing the computational resources
used for the timing tests.
